Priors

### 2024-03-04 analysis/clinical-data.Rmd
First batch of plots and results

source("../utils/plotting.r")
```

@@

```{r}
df <- readRDS("../data-clean/clinical/clinical-data.rds") %>%
  filter(between(month(date), 10, 11))

modeled_days <- list.files("../data-clean/patient-tracking/linked-and-imputed")
modeled_days <- gsub("[[:punct:]]rds", "", modeled_days)
modeled_days <- as.Date(modeled_days)
```

@@

### Diagnosed TB over time

```{r}
diag_tb <- df %>%
  mutate(`Date modeled` = ifelse(date %in% modeled_days, "Yes", "No")) %>%
  group_by(date, `Date modeled`) %>%
  summarize(n_infectious = sum(is_infectious)) %>%
  ungroup()

diag_tb %>%
  ggplot(aes(x = date, y = n_infectious, fill = `Date modeled`)) +
  geom_bar(stat = "identity") +
  scale_x_date(date_labels = "%b %d", breaks = modeled_days) +
  scale_y_continuous(expand = c(0,0)) +
  theme_custom() +
  theme(legend.position = "top")
```

```{r}
diag_tb %>%
  ggplot(aes(x = n_infectious)) +
  geom_histogram()

#' Assumption:
#' Number of diagnosed ~ number of diagnosed TB
#' --> Assume a Dirichlet prior with support according to the counts in the range (1,5).
```

### Suspected TB over time

```{r}
df %>%
  mutate(`Date modeled` = ifelse(date %in% modeled_days, "Yes", "No")) %>%
  group_by(date, `Date modeled`) %>%
  summarize(n_infectious = sum(was_suspected & !is_infectious)) %>%
  ungroup() %>%
  ggplot(aes(x = date, y = n_infectious, fill = `Date modeled`)) +
  geom_bar(stat = "identity") +
  scale_x_date(date_labels = "%b %d", breaks = modeled_days) +
  scale_y_continuous(expand = c(0,0)) +
  theme_custom() +
  theme(legend.position = "top")
```

>>>>

source("utils/plotting.r")
```

@@

```{r}
df <- readRDS("data-clean/clinical/clinical-data.rds") %>%
  filter(between(month(date), 10, 11))

modeled_days <- list.files("data-clean/patient-tracking/linked-and-imputed")
modeled_days <- gsub("[[:punct:]]rds", "", modeled_days)
modeled_days <- as.Date(modeled_days)
modeled_days_abbrv <- format(modeled_days, format = "%b %d")
```

@@

### Diagnosed/Suspected TB over time

```{r}
diag_tb <- df %>%
  mutate(
    date_in_model = format(as.Date(date), format = "%b %d"),
    date_in_model = ifelse(
      date_in_model %in% modeled_days_abbrv, date_in_model,
      "Not modeled"
    ),
    date_in_model = factor(
      date_in_model,
      levels = c(modeled_days_abbrv, "Not modeled")
    )
  ) %>%
  group_by(date, date_in_model) %>%
  summarize(
    n_infectious = sum(is_infectious),
    n_suspected = sum(was_suspected & !is_infectious)
  ) %>%
  ungroup() %>%
  reshape2::melt(c("date", "date_in_model")) %>%
  mutate(
    variable = ifelse(grepl("infectious", variable), "Diagnosed", "Suspected"),
    variable = factor(variable, levels = c("Suspected", "Diagnosed"))
  )

diag_tb_pl <- diag_tb %>%
  ggplot(aes(x = date, y = value, fill = date_in_model, alpha = variable)) +
  geom_bar(position = position_stack(), stat = "identity") +
  scale_x_date(date_labels = "%b %d", breaks = modeled_days) +
  scale_y_continuous(expand = c(0, 0)) +
  scale_fill_manual(values = c(wes_palette("Moonrise3"), "grey")) +
  scale_alpha_discrete(
    breaks = c("Diagnosed", "Suspected"),
    range = c(.33, 1)
  ) +
  labs(
    y = "Number of TB patients attending the clinic"
  ) +
  theme_custom(8) +
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    legend.direction = "vertical",
    legend.box = "vertical",
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    legend.key.width = unit(.2, "cm"),
    legend.key.height = unit(.3, "cm")
  ) +
  guides(
    fill = guide_legend(nrow = 1, order = 2),
    alpha = guide_legend(nrow = 1, order = 1)
  )

save_plot(
  diag_tb_pl,
  pdf_file = "results/data/diagnosed-tb-patients.png",
  w = 16, h = 12
)
```

```{r}
diag_tb %>%
  filter(variable == "Diagnosed") %>%
  ggplot(aes(x = value)) +
  geom_histogram()

table(diag_tb$value[diag_tb$variable == "Diagnosed"])

#' Assumption:
#' Number of diagnosed ~ number of diagnosed TB
#' --> Assume a Dirichlet prior with support according to the counts in the range (1,5).

source("utils/trans_risk.r")

undiag_tb_pl <- data.frame(x = rundiag(1e5)) %>%
  group_by(x) %>%
  summarize(n = n()) %>%
  ungroup() %>%
  mutate(
    p = 100 * n / sum(n),
    p = round(p)
  ) %>%
  ggplot(aes(x = factor(x), y = p)) +
  geom_bar(
    stat = "identity",
    color = wes_palette("GrandBudapest1")[3],
    fill = wes_palette("GrandBudapest1")[4],
    alpha = .5
  ) +
  labs(
    x = "Number of undiagnosed TB patients", y = "Probability (%)"
  ) +
  coord_cartesian(expand = F) +
  scale_y_continuous(limits = c(0, NA)) +
  theme_custom(8) +
  theme(plot.caption = element_text(size = 10))

save_plot(
  undiag_tb_pl,
  pdf_file = "results/inputs/undiagnosed-tb-patients.png",
  w = 8, h = 6
)
```

### 2024-03-04 analysis/environmental-data.Rmd
First batch of plots and results

```{r}
dates <- sort(unique(cont_df$date))
abbr_dates <- paste(month(dates, label = T, abbr = T), day(dates))
cont_df <- readRDS("../data-clean/environmental/continuous-iaq-data.rds") %>%
  mutate(time = as.POSIXct(format(date_time, format = "%H:%M:%S"), format = "%H:%M:%S"),
         date = factor(date, levels = dates))
aer <- readRDS("../data-clean/environmental/air-change-rate.rds") %>%
  mutate(mth = month(date, label = T, abbr= T),
         dy = day(date),
         mthdy = paste(mth, dy),
         mthdy = factor(as.character(mthdy), levels = abbr_dates),
         daytime = factor(daytime, levels = c("Morning", "Afternoon")))
```

@@

```{r}
cont_df %>%
  ggplot(aes(x = time, y = co2, color = date)) +
  geom_step() +
  facet_wrap(~ room) +
  coord_cartesian(expand = F) +
  scale_x_datetime(date_breaks = "1 hour", date_labels = "%H:%M") +
  scale_color_manual(values = wes_palette("Moonrise3")) +
  labs(y = "Number of people in waiting room") +
  theme_custom() +
  theme(axis.title.x = element_blank(),
        legend.title = element_blank())
```

@@

```{r}
aer %>%
  ggplot(aes(x = mthdy, fill = daytime, y = aer)) +
  geom_bar(stat = "identity", position = position_dodge(width = 1, preserve = "single"), width = .66) +
  facet_wrap(~ room) +
  scale_fill_brewer(palette = 9) +
  scale_y_continuous(expand = expansion(mult = c(0, .05))) +
  theme_custom()
```

>>>>

```{r}
dates <- as.Date(c(
  "2021-10-13",
  "2021-10-15",
  "2021-10-25",
  "2021-11-04",
  "2021-11-05"
))
abbr_dates <- format(dates, format = "%b %d")
cont_df <- readRDS("data-clean/environmental/continuous-iaq-data.rds") %>%
  mutate(
    time = as.POSIXct(
      format(date_time, format = "%H:%M:%S"),
      format = "%H:%M:%S"
    ),
    mthdy = factor(
      as.character(format(date, format = "%b %d")),
      levels = abbr_dates
    )
  )
aer <- readRDS("data-clean/environmental/air-change-rate.rds") %>%
  mutate(
    mthdy = factor(
      as.character(format(date, format = "%b %d")),
      levels = abbr_dates
    ),
    daytime = factor(daytime, levels = c("Morning", "Afternoon"))
  )
```

@@

```{r}
co2_pl <- cont_df %>%
  mutate(time = floor_date(time, "10 minutes")) %>%
  group_by(mthdy, time, room) %>%
  summarize(co2 = mean(co2)) %>%
  ungroup() %>%
  mutate(room = factor(
    room,
    levels = c("Waiting room", "Corridor", "TB room")
  )) %>%
  ggplot(aes(x = time, y = co2, color = mthdy)) +
  geom_step() +
  facet_wrap(~room) +
  coord_cartesian(expand = FALSE) +
  scale_x_datetime(date_breaks = "4 hours", date_labels = "%H:%M") +
  scale_color_manual(values = wes_palette("Moonrise3")) +
  labs(
    y = expression("CO"[2] * " (parts per million, ppm)"),
    title = "a"
  ) +
  theme_custom(8) +
  theme(
    axis.title.x = element_blank(),
    legend.title = element_blank(),
    legend.position = "bottom",
    panel.spacing = unit(1, "lines"),
    legend.key.width = unit(0.275, "cm"),
    legend.key.height = unit(0.2, "cm")
  )

save_plot(
  co2_pl,
  pdf_file = "results/data/co2-levels-over-time.png",
  w = 10, h = 6
)
```

@@

```{r}
aer_pl <- aer %>%
  mutate(room = factor(
    room,
    levels = c("Waiting room", "Corridor", "TB room")
  )) %>%
  ggplot(aes(x = room, fill = room, y = aer)) +
  geom_boxplot() +
  # geom_jitter(
  #   mapping = aes(color = daytime),
  #   width = 0.2,
  #   height = 0,
  #   shape = 21
  # ) +
  scale_x_discrete(labels = c("WR", "TB", "CR")) +
  scale_fill_manual(values = wes_palette("Royal2")[-1]) +
  scale_y_continuous(expand = expansion(mult = c(0, .05)), limits = c(0, NA)) +
  labs(
    y = "Air changes per hour",
    title = "b"
  ) +
  theme_custom(8) +
  theme(
    axis.title.x = element_blank(),
    legend.title = element_blank(),
    legend.position = c(0.8, 0.95)
  ) +
  guides(fill = "none")

save_plot(
  aer_pl,
  pdf_file = "results/data/air-changes-per-hour.png",
  w = 6, h = 6
)
```

### 2024-03-04 analysis/patient-tracking.Rmd
First batch of plots and results

source("../utils/plotting.r")
source("../utils/spatial.r")

text_descr <- 8
```

@@

```{r}
df <- readRDS("../data-clean/patient-tracking/augmented-and-combined-data.rds")
```

@@

```{r}
source("../helper/building.R")
```

@@

```{r}
df %>%
  group_by(date, patient_id) %>%
  slice(1) %>%
  ungroup() %>%
  dplyr::select(tracking_end) %>%
  unlist() %>%
  table()

@@

```{r}
time_in_clin <- df %>%
  group_by(date, patient_id) %>%
  summarize(tracking_end = first(tracking_end),
            `Clinic` = n(),
            `Waiting room` = sum(is_waitingroom),
            `TB room` = sum(is_tbroom),
            `Corridor` = sum(is_passage)) %>%
  ungroup() %>%
  mutate(across(c(`Clinic`, `Waiting room`, `TB room`, `Corridor`), ~ .x / 60))

time_in_clin %>%
  ggplot(aes(x = tracking_end, y = total_duration)) +
  geom_boxplot()

time_in_clin %>%
  filter(tracking_end != "Possible HCW") %>%
  dplyr::select(-tracking_end) %>%
  melt(c("date", "patient_id")) %>%
  mutate(variable = factor(variable, levels = c("Clinic", "Waiting room", "TB room", "Corridor"))) %>%
  ggplot(aes(x = variable, fill = variable, y = value)) +
  geom_boxplot() +
  scale_y_sqrt()
```

@@

```{r}
# number of close contacts <1m for >1min
no_close_contacts <- df %>%
  unnest(cols = closeContacts) %>%
  group_by(date, patient_id, closeContacts, tracking_end) %>%
  summarise(n_time = n(),
            tracking_end = first(tracking_end)) %>%
  ungroup() %>%
  group_by(date, patient_id) %>%
  summarize(n_cc = sum(n_time > 60),
            tracking_end = first(tracking_end)) %>%
  ungroup()

time_close_contacts <- df %>%
  mutate(has_closeContact = ifelse(sapply(closeContacts, length) >= 1, T, F)) %>%
  group_by(date, patient_id) %>%
  summarize(cc_time = sum(has_closeContact) / 60,
            tracking_end = first(tracking_end)) %>%
  ungroup()

@@

close_contact %>%
  filter(tracking_end != "Possible HCW") %>%
  ggplot(aes(x = Clinic, y = n_cc)) +
  geom_point()

close_contact %>%
  filter(tracking_end != "Possible HCW") %>%
  ggplot(aes(x = 1, y = cc_time / Clinic)) +
  geom_boxplot() 
```

@@

```{r}
clinic_occupancy <- df %>%
  group_by(date, time) %>%
  summarize(
    `Clinic` = n(),
    `Waiting room` = sum(is_waitingroom),
    `TB room` = sum(is_tbroom),
    `Corridor` = sum(is_passage)) %>%
  ungroup() %>%
  melt(c("date", "time")) %>%
  mutate(variable = factor(variable, levels = c("Clinic", "Waiting room", "TB room", "Corridor")),
         date = format(date, "%b %d"),
         time = as.POSIXct(format(time, format = "%H:%M:%S"), format = "%H:%M:%S")) %>%
  filter(between(hour(time), 7, 16))

clinic_occupancy %>%
  ggplot(aes(x = time, y = value, color = date)) +
  geom_step() +
  facet_wrap(~ variable) +
  coord_cartesian(expand = F) +
  scale_x_datetime(date_breaks = "1 hour", date_labels = "%H:%M") +
  scale_color_manual(values = wes_palette("Moonrise3")) +
  labs(y = "Number of people in waiting room") +
  theme_custom() +
  theme(axis.title.x = element_blank(),
        legend.title = element_blank())
```

@@

```{r}
col <- RColorBrewer::brewer.pal(n = 9, name = "YlOrRd")

plot_spatial <- function(pl) {
  pl +
  ggpubr::background_image(clinic_img) +
  scale_y_continuous(expand = expansion(add=c(1700, 3000)), limits = c(-6500, 2000)) +
  scale_x_continuous(expand = expansion(add=c(400, 500)), limits = c(-16000, 7500)) +
  annotation_custom(entrance_lab, xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf) +
  annotation_custom(wr_lab, xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf) +
  annotation_custom(tb_lab, xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf) +
  annotation_custom(re_lab, xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf) +
  theme_custom() +
  theme(text = element_text(size = text_descr),
        axis.text = element_blank(), axis.title = element_blank(), axis.ticks = element_blank(),
        legend.position = c(0.825,0.05), legend.direction = "horizontal", 
        legend.key.width = unit(0.3, "cm"), legend.key.height = unit(0.2, "cm"),
        panel.background = element_rect(fill = col[1]), panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  guides(fill = guide_legend(title.position = "top"))
}

plot_spatial(
  ggplot(data = df, mapping = aes(x = x, y = y)) +
    geom_bin2d(binwidth = 200) ) +
  labs(fill = "Number of tracks") +
  scale_fill_stepsn(colours = RColorBrewer::brewer.pal(n = 9, name = "YlOrRd"), trans = "log10", 
                    breaks = c(1, 10, 100, 1000, 10000)) 
```

@@

# random sample tracks
ex_pid <- df %>%
  filter(tracking_end != "Possible HCW") %>%
  group_by(day_pid) %>%
  slice(1) %>%
  ungroup() %>%
  group_by(tracking_end) %>%
  sample_n(3) %>%
  ungroup() %>%
  dplyr::select(day_pid) %>%
  unlist()
ex_df <- df %>% filter(day_pid %in% ex_pid)
ex_df_se <- ex_df %>%
  group_by(day_pid) %>%
  slice(1, n()) %>%
  mutate(type = factor(c("Start", "End"), levels=c("Start", "End"))) %>%
  ungroup()

# manual sample of tracks
ex_pid_man <- c(
  "2021-10-25 4649", # Entered + Exited, including TB room stay
  "2021-10-13 6297", # Lost Exit, only waiting room
  "2021-11-04 12860", # (Entered) + Exited, waiting room and corridor
  "2021-10-13 9346", # Entered + Exited, including TB room
  "2021-11-05 16625", # Entered + (Exited), only waiting room
  "2021-10-25 9526", # Lost Exit, waiting room and corridor
  "2021-11-04 9841", # Entered = (Exited), waiting room and corridor
  "2021-10-15 8644", # Entered + Exited, including TB room
  "2021-10-15 9419" # Lost Enter
)
ex_df_man <- df %>% filter(day_pid %in% ex_pid_man)
ex_df_man_se <- ex_df_man %>%
  group_by(day_pid) %>%
  slice(1, n()) %>%
  mutate(type = factor(c("Start", "End"), levels=c("Start", "End"))) %>%
  ungroup()

# plot
plot_spatial(
  ggplot() +
    geom_path(data = ex_df_man, mapping = aes(x = x, y = y), color = "darkred") +
    geom_point(data = ex_df_man_se, mapping = aes(x = x, y = y, shape = type), size = 2) +
    facet_wrap(~ day_pid) +
    scale_shape_manual(values = c(1,13)) 
) +
  theme(legend.position = "none")
```

>>>>

source("utils/plotting.r")
source("utils/spatial.r")
```

@@

```{r}
df <- readRDS("data-clean/patient-tracking/augmented-and-combined-data.rds")

# filter considered clinical attendees
df_matched <- do.call(
  rbind,
  lapply(
    unique(df$date),
    function(d) {
      readRDS(paste0(
        "data-clean/patient-tracking/matched-clinical/",
        d, ".rds"
      ))
    }
  )
) %>%
  mutate(date = as.Date(time))
df_filt <- filter(
  df,
  paste(date, patient_id) %in%
    unique(paste(df_matched$date, df_matched$patient_id))
)
```

@@

```{r}
cellSize <- 250
source("preprocessing/prep_building-rasterize.R")
```

@@

```{r}
track_qual <- df %>%
  group_by(date, patient_id) %>%
  slice(1) %>%
  ungroup() %>%
  dplyr::select(tracking_end) %>%
  unlist() %>%
  table()

sum(track_qual[names(track_qual) != "Possible HCW"])
track_qual_str <- paste0(
  names(track_qual),
  ": ",
  track_qual,
  " (",
  round(track_qual / sum(track_qual) * 100),
  "%)"
)
track_qual_str

@@

```{r}
time_in_clin <- df_filt %>%
  group_by(date, patient_id) %>%
  summarize(
    tracking_end = first(tracking_end),
    `Clinic` = n(),
    `Waiting room` = sum(is_waitingroom),
    `TB room` = sum(is_tbroom),
    `Corridor` = sum(is_passage)
  ) %>%
  ungroup() %>%
  mutate(across(c(`Clinic`, `Waiting room`, `TB room`, `Corridor`), ~ .x / 60))

time_in_clin_pl <- time_in_clin %>%
  filter(tracking_end != "Possible HCW") %>%
  dplyr::select(-tracking_end) %>%
  melt(c("date", "patient_id")) %>%
  mutate(variable = factor(
    variable,
    levels = c("Clinic", "Waiting room", "TB room", "Corridor")
  )) %>%
  ggplot(aes(x = variable, fill = variable, y = value)) +
  geom_boxplot() +
  scale_y_sqrt(breaks = c(0, 1, 10, 30, 60, 120, 180)) +
  scale_x_discrete(labels = c("Clinic", "WR", "TB", "CR")) +
  scale_fill_manual(values = wes_palette("Royal2")) +
  labs(
    y = "Time in clinic (minutes)",
    title = "c"
  ) +
  theme_custom(8) +
  theme(
    legend.position = "none",
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    plot.title.position = "plot"
  )

save_plot(
  time_in_clin_pl,
  pdf_file = "results/data/time-in-clinic.png", w = 5.3, h = 6
)
```

@@

```{r}
# number of close contacts <1m for >1min
no_close_contacts <- df_filt %>%
  unnest(cols = closeContacts) %>%
  group_by(date, patient_id, closeContacts, tracking_end) %>%
  summarise(
    n_time = n(),
    tracking_end = first(tracking_end)
  ) %>%
  ungroup() %>%
  group_by(date, patient_id) %>%
  summarize(
    n_cc = sum(n_time > 60),
    tracking_end = first(tracking_end)
  ) %>%
  ungroup()

time_close_contacts <- df_filt %>%
  mutate(has_closeContact = ifelse(
    sapply(closeContacts, length) >= 1, T, F
  )) %>%
  group_by(date, patient_id) %>%
  summarize(
    cc_time = sum(has_closeContact) / 60,
    tracking_end = first(tracking_end)
  ) %>%
  ungroup()

@@

cc_n_pl <- close_contact %>%
  filter(tracking_end != "Possible HCW") %>%
  ggplot(aes(x = n_cc)) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    y = "Density", x = "Number of close contacts",
    title = "d"
    # subtitle = "Defined as <1m for >1min"
  ) +
  geom_density(fill = wes_palette("FantasticFox1")[2], color = wes_palette("FantasticFox1")[2], alpha = 0.8) +
  theme_custom(8) +
  theme(
    plot.title.position = "plot",
    plot.margin = margin(r = 11),
    plot.subtitle = element_text(margin = margin(b = 11))
  )

save_plot(
  cc_n_pl,
  pdf_file = "results/data/number-close-contacts.png", w = 5.3, h = 6
)

cc_t_pl <- close_contact %>%
  filter(tracking_end != "Possible HCW") %>%
  ggplot(aes(x = cc_time / Clinic * 100)) +
  scale_x_continuous(expand = c(0, 0), limits = c(0, 100)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    y = "Density",
    x = "Time in close contact (%)",
    title = "e"
  ) +
  geom_density(
    fill = wes_palette("Moonrise1")[2],
    color = wes_palette("Moonrise1")[2],
    alpha = 0.8
  ) +
  theme_custom(8) +
  theme(
    plot.title.position = "plot",
    plot.margin = margin(r = 11)
  )

save_plot(
  cc_t_pl,
  pdf_file = "results/data/time-close-contacts.png", w = 5.3, h = 6
)
```

@@

```{r}
clinic_occupancy <- df %>%
  group_by(date, time) %>%
  summarize(
    `Clinic` = n(),
    `Waiting room` = sum(is_waitingroom),
    `TB room` = sum(is_tbroom),
    `Corridor` = sum(is_passage)
  ) %>%
  ungroup() %>%
  melt(c("date", "time")) %>%
  mutate(
    variable = factor(
      variable,
      levels = c("Clinic", "Waiting room", "TB room", "Corridor")
    ),
    date = format(date, "%b %d"),
    date = factor(
      as.character(date),
      levels = c("Oct 13", "Oct 15", "Oct 25", "Nov 04", "Nov 05")
    ),
    time = as.POSIXct(format(time, format = "%H:%M:%S"), format = "%H:%M:%S")
  ) %>%
  filter(between(hour(time), 7, 16))

time_pl <- clinic_occupancy %>%
  filter(variable == "Clinic") %>%
  ggplot(aes(x = time, y = value, color = date)) +
  geom_step() +
  # ggh4x::facet_wrap2(~variable, axes = "x", remove_labels = "all") +
  coord_cartesian(expand = FALSE) +
  scale_x_datetime(date_breaks = "3 hours", date_labels = "%H:%M") +
  scale_color_manual(values = wes_palette("Moonrise3")) +
  labs(
    y = "Number of people in clinic",
    title = "f"
  ) +
  theme_custom(8) +
  theme(
    axis.title.x = element_blank(),
    legend.title = element_blank(),
    legend.position = "bottom",
    legend.key.width = unit(0.275, "cm"),
    legend.key.height = unit(0.2, "cm")
  )

save_plot(
  time_pl,
  pdf_file = "results/data/no-people-over-time.png",
  w = 8, h = 6
)
```

@@

```{r}
spatial_pl <- plot_spatial(
  ggplot(data = df, mapping = aes(x = x, y = y)) +
    geom_bin2d(binwidth = 200),
  text_descr = 8
) +
  labs(
    fill = "Number of tracks",
    title = "g"
  ) +
  scale_fill_gradientn(
    colours = RColorBrewer::brewer.pal(n = 9, name = "YlOrRd"),
    trans = "log10",
    labels = scales::comma,
    breaks = c(1, 10, 100, 1000, 10000)
  ) +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal",
    legend.key.height = unit(0.2, "cm"),
    legend.key.width = unit(1, "cm")
  ) +
  guides(fill = guide_colorbar(title.vjust = 1))

save_plot(
  spatial_pl,
  pdf_file = "results/data/no-people-spatial.png",
  w = 8, h = 6
)
```

@@

# random sample tracks
ex_pid <- df %>%
  filter(tracking_end != "Possible HCW") %>%
  group_by(day_pid) %>%
  slice(1) %>%
  ungroup() %>%
  group_by(tracking_end) %>%
  sample_n(3) %>%
  ungroup() %>%
  dplyr::select(day_pid) %>%
  unlist()
ex_df <- df %>% filter(day_pid %in% ex_pid)
ex_df_se <- ex_df %>%
  group_by(day_pid) %>%
  slice(1, n()) %>%
  mutate(type = factor(c("Start", "End"), levels = c("Start", "End"))) %>%
  ungroup()

# manual sample of tracks
ex_pid_man <- c(
  "2021-10-25 4649", # Entered + Exited, including TB room stay
  "2021-10-13 6297", # Lost Exit, only waiting room
  "2021-11-04 12860", # (Entered) + Exited, waiting room and corridor
  "2021-10-13 9346", # Entered + Exited, including TB room
  "2021-11-05 16625", # Entered + (Exited), only waiting room
  "2021-10-25 9526", # Lost Exit, waiting room and corridor
  "2021-11-04 9841", # Entered = (Exited), waiting room and corridor
  "2021-10-15 8644", # Entered + Exited, including TB room
  "2021-10-15 9419" # Lost Enter
)
ex_df_man <- df %>% filter(day_pid %in% ex_pid_man)
ex_df_man_se <- ex_df_man %>%
  group_by(day_pid) %>%
  slice(1, n()) %>%
  mutate(type = factor(c("Start", "End"), levels = c("Start", "End"))) %>%
  ungroup()

# plot
ex_tracks <- plot_spatial(
  ggplot() +
    geom_path(
      data = ex_df_man,
      mapping = aes(x = x, y = y),
      color = "darkred"
    ) +
    geom_point(
      data = ex_df_man_se,
      mapping = aes(x = x, y = y, shape = type),
      size = 2
    ) +
    facet_wrap(~day_pid, ncol = 3) +
    scale_shape_manual(values = c(1, 13)),
  text_descr = 8
) +
  theme(
    legend.position = "none"
  )

save_plot(
  ex_tracks,
  pdf_file = "results/data/example-patient-tracks.png",
  w = 16, h = 12
)
```

### 2024-03-04 illustrations/priors.Rmd
First batch of plots and results

```{r}
library(tidyverse)
library(LaplacesDemon)
source("../utils/trans_risk.r")
source("../utils/plotting.r")
```

## Quanta

```{r}
q_dat <- data.frame(x = seq(0, 200, 0.1)) %>%
  mutate(y = pq(x))

prev_est <- data.frame(
  study = c("Andrews (2014)", "Escombe (2008)", "Nardell (1991)", "Riley (1962)"),
  x = c(0.89, 8.2, 12.5, 1.25)
) %>%
  mutate(y = pq(x))

q_pl <- ggplot(mapping = aes(x = x, y = y)) +
  geom_line(data = q_dat, direction = "vh") +
  geom_segment(data = prev_est, mapping = aes(xend = x, yend = 0, color = study), linetype = "dotted") +
  geom_segment(data = prev_est, mapping = aes(yend = y, xend = 0, color = study), linetype = "dotted") +
  geom_point(data = prev_est, mapping = aes(color = study), shape = 17, size = 2) +
  geom_text(data = prev_est, mapping = aes(label = study, color = study), size = 8 / cm(1), nudge_x = log(1.35)) +
  scale_x_continuous(expand = expansion(mult = c(0,.025)), breaks = c(0, 1, 10, 100, 200), trans = scales::pseudo_log_trans(base = 10)) +
  scale_y_continuous(expand = c(0,0), labels = scales::percent_format(suffix = "")) +
  scale_color_manual(values = wes_palette("Cavalcanti1")) +
  labs(x = "Quanta generation rate (quanta/h)", y = "Cumulative probability (%)") +
  theme_custom() +
  theme(legend.position = "none")

q_pl
save_plot(q_pl, pdf_file = "../illustrations/prior-q.pdf", w = 12, h = 8)
```

## Viral inactivation rate

```{r}
plambda <- function(x, disease = "TB") {
  #LaplacesDemon::ptrunc(x, spec = "st", a = 0, b = 10, mu = 0.5, sigma = 1, nu = 5)
  plnorm(x, meanlog = log(0.5), sdlog = 1)
}

lambda_dat <- data.frame(x = seq(0, 10, .01)) %>%
  mutate(y = plambda(x))

prev_est_vir <- data.frame(
  study = c("Loudon (1969)", "Lever (2000)", "Gannon (2007)"),
  x = c(0.12, 8.3, 0.46)
) %>%
  mutate(y = plambda(x))

lambda_pl <- ggplot(mapping = aes(x = x, y = y)) +
  geom_line(data = lambda_dat, direction = "vh") +
  geom_segment(data = prev_est_vir, mapping = aes(xend = x, yend = 0, color = study), linetype = "dotted") +
  geom_segment(data = prev_est_vir, mapping = aes(yend = y, xend = 0, color = study), linetype = "dotted") +
  geom_point(data = prev_est_vir, mapping = aes(color = study), shape = 17, size = 2) +
  geom_text(data = prev_est_vir %>% dplyr::filter(study != "Lever (2000)"), mapping = aes(label = study, color = study), size = 8 / cm(1), nudge_x = log(1.35), nudge_y = .02) +
  geom_text(data = prev_est_vir %>% dplyr::filter(study == "Lever (2000)"), mapping = aes(label = study, color = study), size = 8 / cm(1), nudge_y = 0.05) +
  scale_x_continuous(expand = expansion(mult = c(0,.025)), breaks = c(0, 0.5, 1, 2, 5, 10), trans = scales::pseudo_log_trans(base = 10)) +
  scale_y_continuous(expand = expansion(mult = c(0,.025)), labels = scales::percent_format(suffix = "")) +
  scale_color_manual(values = wes_palette("Cavalcanti1")) +
  labs(x = "Viral inactivation rate (quanta/h)", y = "Cumulative probability (%)") +
  theme_custom() +
  theme(legend.position = "none")

lambda_pl
save_plot(lambda_pl, pdf_file = "../illustrations/prior-lambda.pdf", w = 12, h = 8)
```

>>>>

```{r}
library(tidyverse)
library(LaplacesDemon)
source("utils/trans_risk.r")
source("utils/plotting.r")
```

## Generation rate

```{r}
set.seed(12345)

q_dat <- rbind(
  data.frame(
    x = rq(bact_load.mtb(1e6), activity = "waiting"),
    activity = "Waiting"
  ),
  data.frame(
    x = rq(bact_load.mtb(1e6), activity = "walking"),
    activity = "Walking"
  )
)

q_dat %>%
  group_by(activity) %>%
  tidybayes::median_qi(x, .width = .5)

q_dat_dens <- q_dat %>%
  group_by(activity) %>%
  summarize(dens = list(density(x, adjust = 2)))

prev_est <- data.frame(
  study = c(
    "Andrews (2014)",
    "Escombe (2008)",
    "Nardell (1991)",
    "Riley (1962)"
  ),
  x = c(0.89, 8.2, 12.5, 1.25),
  y = c(1, 7, 9, 3) / 1e2
) %>%
  mutate(lab = paste0(study, ": ", round(x, 2)))

q_pl <- ggplot() +
  geom_density(
    data = q_dat,
    mapping = aes(x = x, linetype = activity),
    adjust = 2
  ) +
  geom_segment(
    data = prev_est,
    mapping = aes(x = x, xend = x, y = 0, yend = y, color = study),
    linetype = "dotted"
  ) +
  geom_point(
    data = prev_est,
    mapping = aes(x = x, color = study, y = y),
    shape = 17, size = 2
  ) +
  geom_text(
    data = prev_est,
    mapping = aes(x = x, label = lab, color = study, y = y),
    size = 8 / cm(1), vjust = -2, hjust = 1
  ) +
  scale_x_log10(
    expand = expansion(mult = c(0, .025)),
    breaks = c(1e-4, 1e-5, 1e-3, 1e-2, 1e-1, 1e0, 1e1, 1e2, 1e3, 1e4, 1e5)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    labels = scales::percent_format(suffix = "")
  ) +
  scale_color_manual(values = wes_palette("Cavalcanti1")) +
  labs(
    x = "Quanta generation rate (quanta/h)",
    y = "Density"
  ) +
  theme_custom() +
  theme(legend.position = "none")

save_plot(
  q_pl,
  pdf_file = "results/inputs/quanta-generation-rate.png",
  w = 16, h = 12
)
```

## Inactivation rate

```{r}
set.seed(12345)

lambda_dat <- data.frame(x = rlambda(1e6))

lambda_dat %>%
  tidybayes::median_qi(x, .width = .5)

prev_est_vir <- data.frame(
  study = c(
    "Loudon (1969)",
    "Lever (2000)",
    "Gannon (2007)",
    "Klein (2014)"
  ),
  x = c(
    log(2) / 6,
    log(2) / (5 / 60),
    log(2) / 1.5,
    log(2) / (0.5 / (log(20 / 100, 0.5)))
  ),
  y = c(15, 5, 10, 20) / 1e2
) %>%
  mutate(lab = paste0(study, ": ", round(x, 2)))

lambda_pl <- ggplot() +
  geom_density(
    data = lambda_dat,
    mapping = aes(x = x),
    adjust = 2
  ) +
  geom_segment(
    data = prev_est_vir,
    mapping = aes(x = x, xend = x, y = 0, yend = y, color = study),
    linetype = "dotted"
  ) +
  geom_point(
    data = prev_est_vir,
    mapping = aes(x = x, color = study, y = y),
    shape = 17, size = 2
  ) +
  geom_text(
    data = prev_est_vir,
    mapping = aes(x = x, label = lab, color = study, y = y),
    size = 8 / cm(1), vjust = -2
  ) +
  scale_x_log10(
    expand = expansion(mult = c(0, .025)),
    breaks = c(1e-4, 1e-5, 1e-3, 1e-2, 1e-1, 1e0, 1e1, 1e2, 1e3, 1e4, 1e5)
  ) +
  scale_y_continuous(
    expand = expansion(mult = c(0, .05)),
    labels = scales::percent_format(suffix = "")
  ) +
  scale_color_manual(values = wes_palette("Cavalcanti1")) +
  labs(
    x = "Bacterial inactivation rate (quanta/h)",
    y = "Density"
  ) +
  theme_custom() +
  theme(legend.position = "none")

save_plot(
  lambda_pl,
  pdf_file = "results/inputs/bacterial-inactivation-rate.png",
  w = 16, h = 12
)
```
